Nanophotonic Computational Design

### 2013-02-20 defense/pres2.tex
Getting there...

\I  The full parameter space is \emph{vast}
\smallfig{des_complexity}
\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities
    \BI A virtually uncountable number 
    \I  Can only be design by a computer \EI
\nextpage

\smallfig{takeaway}
\I  Our work: Software to design full 3D, multi-mode, and multi-functional
    linear nanophotonic devices---using the fully available parameter space \pause
\I  Many of these devices are
    \BI Completely novel (no previously known designs)
    \I  Extremely compact (footprints of a few vacuum wavelengths)
    \I  High efficiency ($>80\%$ transmission) \EI
\nextpage

@@

@@

\oursection{Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  Goal: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, manufacturable structure \EI
\nextpage

@@

\oursection{Maxwell: Light-simulation supercomputer}
\I  Partnered with Wonseok to develop a cloud-based electromagnetic solver 
    using Amazon Web Services 
    \BI GPU-accelerated implementation of Wonseok's algorithm
    \I  Cluster scales automatically to tens of nodes \EI
\nextpage

@@

\I  The key technological enabler ...

>>>>

\I  The full parameter space is \emph{vast}
\smallfig{des_complexity}
\I  Include/exclude per pixel gives us $2^{(15^2)} = 2^{225}$ possibilities
    \BI A virtually uncountable number 
    \I  Can only be leveraged computationally \EI
\nextpage

\smallfig{takeaway}
\I  Our work: Software to design 3D linear nanophotonic devices using 
    the full available parameter space \pause
\I  Many of these devices are
    \BI Completely novel (no previously known designs)
    \I  Extremely compact (footprints of a few vacuum wavelengths)
    \I  High efficiency ($>80\%$ transmission) \EI
\nextpage

@@

\I  Called \emph{objective-first} design because the design objective 
    is prioritized above the physics residual
    \begin{align*} 
    \minimize & \|A(z)x - b\|^2 \\
    \subto & x_\text{boundary} - \hat{x}_\text{boundary} = 0 \\
        & z_\text{min} \le z \le z_\text{max}
    \end{align*}
% \I  In contrast, the typical formulation is 
%     \begin{align*} 
%     \minimize & \|x_\text{boundary} - \hat{x}_\text{boundary}\|^2 \\
%     \subto & A(z)x - b  = 0 \\
%         & z_\text{min} \le z \le z_\text{max}
%     \end{align*}
\nextpage

@@

\oursection{Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  Goal: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, planar, manufacturable structure \EI
\nextpage

@@

\oursection{Maxwell: Light-simulation supercomputer}
\I  Partnered with Wonseok to develop a cloud-based electromagnetic solver 
    using Amazon Web Services 
    \BI GPU-accelerated implementation of Wonseok's algorithm
    \I  Cluster scales automatically to tens of nodes \EI
\smallfig{maxwell}
\nextpage

@@

\I  The key technological enabler in achieving 3D design
\nextpage

\oursection{3D design: problem statement}
\begin{align*}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align*}
\I  $M$ modes with $N_i$ monitored output modes each
    \BI $b_i$ is the input excitation for each mode
    \I  $|c_{ij}\T x_i|$ is the field overlap with output mode $c_{ij}$
    \I  $\alpha_{ij}$ and $\beta_{ij}$ is the design range for the overlap \EI
\nextpage

\I  Show input and output modes here as explanation of problem statement
\I  Use 3D model of wgc_te as example.
\nextpage
